\mytitile\\~

### 2019-10-23 document.tex
AppenB

\subsection{Experiment}

\subsubsection{Device design and fabrication}
We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states. In \autoref{fig:experiment}~(a) the optical photograph of the device is shown depicting the layout of the components. The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed. In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler. Flux lines that allow independent control of the $ge$ transitions of the transmons are coming from the sides. Finally, the excitation waveguide coming from below directs microwave signal towards the SAM. In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device. The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances. The capacitively coupled excitation line is also shown in green. Finally, in \autoref{fig:experiment}~(c) we show schematically the $ge$ transitions of the transmons depending on the external magnetic flux. Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue). Using both coils, it is possible to align them so that the lower sweet-spot of the orange qubit. As will be shown, this arrangement allows to see multiple energy level intersections including higher transmon levels, and thus we are measuring the SAM in the region shown with the dashed rectangle.

\begin{figure}
	\includegraphics[width=\linewidth]{experiment}
	\caption{Experimental device. \textbf{(a)} Optical photograph of the device (false coloured). Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator. From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green). \textbf{(b)} The equivalent electrical circuit. Tunable Josephson junctions are in fact SQUIDs with magnetic flux control. \textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly). In this work, we concentrate on the area inside the dashed rectangle.}
	\label{fig:experiment}
\end{figure}

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & 250 & 250 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
\end{table}

@@

\renewcommand{\kbldelim}{(}% Left delimiter
\renewcommand{\kbrdelim}{)}% Right delimiter
\begin{widetext}
	\begin{equation}\label{matrix} 
	\text{$H^R$} = \kbordermatrix{
	\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
	0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
	\text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
			$} t}/2 \\
	0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
}
	\end{equation}
\end{widetext}
Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{tr1}=0$,$\Delta_2 = \omega_d-\omega_{tr2}$.
Let's consider the Hamiltonian (\autoref{matrix}) in details. Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
\begin{equation}
	H^R=H_0+V_J+V_t
\end{equation}
The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$.
The Hamiltonian $H_0$ is station and we can find eigenvectors and eigenvalues. The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width os the dressed states.
Firstly, we consider the system of non-interacting qubits $(J=0)$. In this case some transitions are prohibited and the splitting we are interested in is not observed. 
Therefore a non-zero interaction between qubits is necessary to observe AT effect.

@@

\section{Theoretical description of two-photon process}
Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.

Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$ . After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$. The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$. A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
\begin{equation}\label{forpsi}
	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
\end{equation}

The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest. Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.

Solving \autoref{forpsi} by simple iteration gives the series solution
\begin{equation}
	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
\end{equation}
\begin{equation}
	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
\end{equation}
For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
In our case the interaction in interaction picture satisfies the following relation
\begin{equation}
	\begin{split}
	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
	\end{split}
\end{equation}
Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
\begin{equation}
	\begin{split}
	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
	\end{split}
\end{equation}
To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
	\end{split}
\end{equation}
Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
	\end{split}
\end{equation}

@@

 Let's described the anti-crossing highlighted in red in the picture.

>>>>

\subsection{Experiment}
\subsubsection{Device design and fabrication}
The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons. Qubit control is achieved by external microwave driving line and two flux bias lines.

\begin{figure}
	\includegraphics[width=\linewidth]{experiment}
	\caption{Experimental details. \textbf{(a)} Sample optical photograph \textbf{(b)} Electrical scheme \textbf{(c)} Spectral lines of the qubits}
\end{figure}

@@

\renewcommand{\kbldelim}{(}% Left delimiter
\renewcommand{\kbrdelim}{)}% Right delimiter
\begin{widetext}
	\begin{equation}\label{matrix} 
	\text{$H^R$} = \kbordermatrix{
	\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
	0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
	\text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
			$} t}/2 \\
	0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
}
	\end{equation}
\end{widetext}
Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{1}=0$,$\Delta_2 = \omega_d-\omega_{2}$, $\delta_{\omega} = \omega_{dr1}-\omega_{dr2}$.
Let's consider the Hamiltonian (\autoref{matrix}) in details. Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
\begin{equation}
	H^R=H_0+V_J+V_t
\end{equation}
The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$, which is stationary, so the levels can be found and schematically depicted in \autoref{fig:main_scheme}~(b). The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width off the dressed states.
Firstly, we consider the system of non-interacting qubits $(J=0)$. In this case some transitions are prohibited and the splitting we are interested in is not observed. 
Therefore a non-zero interaction between qubits is necessary to observe AT effect.

@@

\section{Theoretical description of two-photon process}
Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.

Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$. After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\tilde{\psi}(t)}{t}=\tilde{V}(t)\tilde{\psi}(t)$. The reference states of $H_0$ will be denoted as $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$. A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
\begin{equation}\label{forpsi}
	\tilde{\psi_i}(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\tilde{\psi_i}(t_1)}
\end{equation}

Mainly important for us is to find not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state. Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.

Solving \autoref{forpsi} by simple iteration gives the series solution
\begin{equation}
	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
\end{equation}
\begin{equation}
	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
\end{equation}
For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
In our case the interaction in interaction picture satisfies the following relation
\begin{equation}
	\begin{split}
	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
	\end{split}
\end{equation}
Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
\begin{equation}
	\begin{split}
	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
	\end{split}
\end{equation}
To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
	\end{split}
\end{equation}
Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
	\end{split}
\end{equation}
The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude. So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
\begin{equation}
	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
\end{equation}
For simplifier the equation we have made use of the relation:
\begin{equation}\nonumber
	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
\end{equation} 
For $\omega_f=\omega_i+2\omega_d$.
\begin{equation}
	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)
\end{equation}

@@
